%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Systems Engineer II} % Job title
    {Raytheon Missiles \& Defense} % Organization
    {Tucson, AZ} % Location
    {Jun. 2021 – Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical lead on a project to automate training and deployment of neural networks on embedded hardware.}
        \item {Spearheaded customer demonstrations and coordinated project timelines of third-party contractors.}
        \item {Owned the machine learning component of an Unmanned Aerial Systems (UAS) program. Ensured functionality of software ahead of flight tests and analyzed test data to evaluate accuracy and enhance the model.}
        \item {Conducted research and development of neural networks for image classification.}
        \item {Jumpstarted effort to upgrade company-wide internal libraries from RHEL7 to RHEL8.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AI \& ML Software Engineering Intern} % Job title
    {Advanced Micro Devices (AMD)} % Organization
    {Austin, TX} % Location
    {May – Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an algorithm to predict the results of simulated benchmarks up to a week in advance.}
        \item {Key contributor to a paper on benchmark prediction submitted to an internal ML conference.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {CAL Analytics} % Organization
    {Columbus, OH} % Location
    {May – Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created internal Python tools to automatically convert and analyze large datasets of aircraft trajectory and sensor data.}
        \item {Developed 3D geospatial visualizations for aircraft and satellites in CesiumJS.}
        \item {Generated photorealistic images in Blender to train DeepLabv3 for autonomous aerial navigation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {} % Organization
    {Dayton, OH} % Location
    {May - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led an initiative for a hardware-in-the-loop testbed on ODROID using ArduCopter and UxAS.}
        \item {Debugged and extended functionality of existing AFSIM tools and also created new tools.}
        \item {Ported software from Windows to Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {} % Organization
    {} % Location
    {May – Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and validated stochastic models of aircraft radar and INS/GPS systems in C++ for AFSIM.}
        \item {Created data visualization tools in Matlab for large trajectory datasets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lab Assistant II} % Job title
    {Lumir Research Institute} % Organization
    {Dayton, OH} % Location
    {Jun. – Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-led team developing data visualizations for diabetes patients in collaboration with Humana.}
        \item {Developed an internal application for processing GIS imagery using Qt and OpenGL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Wright Scholar Research Assistant} % Job title
    {Wright-Patterson AFB} % Organization
    {Dayton, OH} % Location
    {Jun. – Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led team developing prototype indoor positioning system using COTS technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
